Paradigms in Physics 2.0

### 2017-06-27 paper.tex
start tweaking intro to match 3 big ideas

\section{Introduction}
Basic Paradigms in Physics ideas:
\begin{enumerate}
\item Attention to sequencing of concepts (and articulating content
  learning goals)
\item Faculty buy in and understanding of the sequencing and goals
\item Active engagement
\end{enumerate}
\emph{This} is the Paradigms.  \emph{Explain why our 2.0 changes were
  made, how they addressed these principles.  (i.e. sophomore-year
  courses, math bits, giving students more electives as seniors) Also
  articulate the process (both 1.0 and 2.0) in terms of these big
  ideas.}

The Paradigms in Physics program began around the time when our
current students were born~\cite{manogue2001paradigms}.  The time has
arrived for a change.  Over the years, we have identified a number of
problems in our curriculum that we were unable to address without
addressing the physics major curriculum as a whole.  In this paper, we
share the motivation for our Paradigms 2.0 effort, the process by
which we achieved consensus on an improved curriculum, and will give
a summary and a few highlights of the new program.

@@

\subsection{Motivation for Paradigms 2.0}
There were a number of factors that motivated us to embark on the
Paradigms~2.0 process.  The original Paradigms in Physics curricular
reform from 200? was showing its age.  In the intervening years we
have made a large number of modifications, such as reordering
Paradigms, introducing one new Paradigm, and introducing and changing
computational physics courses.

\paragraph{Transfer students}
Our curriculum is strongly affected by our desire to accomodate
transfer students from community colleges.  This leads us to focus on
a physics major in which all upper-division courses are taken in two
years.  However, our current curriculum is very hard on students in
the fall of their junior year, and especially so for transfer
students.  So we hoped to structure the courses such that non-transfer
students could be better prepared for their junior year, while
transfer students could postpone a few courses so that their junior
Fall would be no more difficult than that of any other student.

>>>>

\section{Introduction}
The Paradigms in Physics program is a rethinking of the upper-division
physics curriculum that began around the time when our current
students were born~\cite{manogue2001paradigms}.  The basic ideas
behind the original Paradigms reform were (1) attention to the
sequencing of concepts, (2) acheiving faculty buy-in, which requires
faculty to understand the sequencing, and (3) implementation of active
engagement through the upper-division curriculum.  In 2016, we began a
rethinking of the Paradigms, with focus on the same principles guiding
the original effort, but with the input of new faculty, and applying
lessons learned over the past two decades.  In this paper, we will
explain the reasoning behind this Paradigms 2.0 effort, the process by
which we achieved developed and reached consensus on an improved
curriculum, and will give both a summary and a few highlights of the
new program.

@@

\subsection{Motivation for Paradigms 2.0}
There were a number of factors that motivated us to embark on the
Paradigms~2.0 process.  In the last two decades, we have observed
challenges students face in the Paradigms.  While in many cases we
addressed these by changing and reordering the courses, we felt a look
at the entire curriculum was in order.  In addition, our faculty
buy-in and aware was diminishing by attrition: while our younger
faculty are enthusiastic about the Paradigms, many lack perspective on
where students are in a given course, and what content is essential
for students to grasp prior to a following course.

\paragraph{Transfer students}
Our curriculum is strongly affected by our desire to accomodate
transfer students from community colleges.  This leads us to focus on
a physics major in which all upper-division courses are taken in two
years.  However, our current curriculum is very hard on students in
the fall of their junior year, and especially so for transfer
students.  So we aimed to structure the courses such that non-transfer
students could be better prepared for their junior year, while
transfer students could postpone a few courses so that their junior
Fall would be no more difficult than that of any other student.
